Brief Announcement: Tight Bounds for Online Balanced Repartitioning

### 2020-03-27 paper/paper.tex
Fig description
Rewrite

\maciek{Sketch only}

We reduce the paging problem with the universe $U$ of size $2k$ and the cache of size $2k-1$.
Recall that the lower bound for the competitive ratio for such paging problem is $2k-1$.

\begin{theorem}
  Every deterministic algorithm for BRP with $\ell=2$ is at least $c$-competitive, where $c=2k-1$.
\end{theorem}

\begin{proof}
We partition nodes into $3$ sets: $A$, $B$ and $C$.
Sets has the following cardinality: $|A| = k-1$, $|B| = k-1$, and $|C| = 2$.
We arbitrarily assign all elements of the universe $U$ to nodes from $A\cup B\cup C$.

Note that in every configuration, at least one of these sets is split, i.e., is not completely contained in one cluster.
Intuitively, if a node is split from other nodes of any of sets $A,B,C$, then it is outside of the cache.

Similarly to the lower bound TODO ref $\Omega(kl)$, we construct components of nodes, and issue the requests if the algorithm splits the component.
(In the current proof, the components produced are oblivious to the configuration of the algorithm, yet the requests issued depend on if the algorithm splits the components. In $\Omega(kl)$, the components were constructed upon the actions of the algorithm, too.)

Now, we show how to simulate an algorithm for the paging problem using the constructed BRP instance.
Fix any algorithm for the paging problem.
If a request to element $e$ comes, we identify its corresponding node $v_e$, and the set $S$ from $A,B,C$ that contains it.
Then, the adversary produces a component $S$, and removes it right after the algorithm collocates the whole $S$ on one cluster.

>>>>

\maciek{TODO: splitting nodes explain in the preliminaries}

We show the reduction from the paging problem with the universe $U$ of size $2k$ and the cache of size $2k-1$.
Recall that the lower bound for the competitive ratio for such paging problem is $2k-1$.

Similarly to the lower bound TODO ref $\Omega(kl)$, we construct components of nodes, and issue the requests if the algorithm splits the component.
In the proof in this section, the components produced are oblivious to the configuration of the algorithm, yet the requests issued depend on if the algorithm splits the components. In $\Omega(kl)$ LB, the components were constructed upon the actions of the algorithm, too.

\maciek{TODO: a figure of 3 sets split.}

\begin{theorem}
  No deterministic algorithm for BRP with two clusters can achieve a competitive ratio smaller than $2k-1$.
\end{theorem}

\begin{proof}
We partition nodes into $3$ sets $A$, $B$, and $C$.
Sets have cardinalities $|A| = k-1$, $|B| = k-1$, and $|C| = 2$.
Each element $e$ of the universe $U$ have a corresponding node $v_e \in A\cup B\cup C$.

Intuitively, if a node is split from other nodes of any of sets $A,B,C$, then it is outside of the cache.
Note that in every configuration, at least one of these sets is split.

For any sequence of paging requests, we produce a corresponding BRP pairwise request sequence.
To this end, fix an algorithm ALG for the paging problem.
When a request to element $e$ comes, we identify the set $S \in \{ A,B,C \}$ that contains the corresponding node $v_e$.
Then, the adversary forms a component $S$, and dismisses it right after the algorithm collocates the whole $S$ on one cluster.
Recall that forming a component means that the adversary continuously issues requests to any two nodes of a component that are split.
